---
title: "<center>**scaRy_R**</center>"
author: "<center>Wyclife Agumba Oluoch</center>"
date: '<center>`r Sys.time()`</center>'
bibliography: 
  - bib/packages.bib
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: darkly
    #highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
packages <- c("base",
              'knitr',
              'rmarkdown',
              'prettydoc')
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}
lapply(packages, library, character.only = TRUE) |> invisible()
```

```{r write_bib, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```

# Introduction

I write this blog as a reflection of my personal journey in learning `R` as a programming language. I, therefore, intend it to be read by seasoned R users as well as new R users whom have not even downloaded the program, just to have a glimpse of the reality that lies ahead.

Learning `R`, like any other programming language, is normally received by learners with awe. Why? Because it normally comes from people with experience, who have used the program for a long time that they forget how a new user should get into the learning process. 

# Challenges faced by new learners.

 - We cannot teach you everything in `R`. 
 
 - From the basics we have given you, it is now upon you to explore more and learn.
 
 - Now you can fetch your own data and rerun the scripts.
 
 - All the scripts are available on GitHub repository.

These are some of the statements that return potential `R` users back to regular spreadsheets.

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Conclusion
