---
title: "<center>**scaRy_R**</center>"
author: "<center>Wyclife Agumba Oluoch</center>"
date: '<center>`r Sys.time()`</center>'
bibliography: 
  - bib/packages.bib
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: cerulean # darkly, cerulean, united
    highlight: haddock
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
packages <- c("base",
              'knitr',
              'rmarkdown',
              'prettydoc')
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}
lapply(packages, library, character.only = TRUE) |> invisible()
```

```{r write_bib, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```

# Introduction

I write this blog as a reflection of my personal journey in learning `R` as a programming language. I will use **`r version[['version.string']]`** throughout the blog. I intend it to be read by seasoned R users as well as new R users whom have not even downloaded the program, just to have a glimpse of the reality that lies ahead.

Learning `R`, like any other programming language, is normally received by learners (especially those with _zero_ background in programming) with awe. Why? Because it normally comes from people with experience, who have used the program for a long time that they forget how a new user should get into the learning process. 

# ScaRy comments

 - <small>We cannot teach you everything in `R` `r emo::ji("face")`</small>. 
 
 - From the basics we have given you, it is now upon you to explore more and learn `r emo::ji("cry")`.
 
 - Now you can fetch your own data and rerun the scripts `r emo::ji("sad")`.
 
 - All the scripts are available on GitHub repository.
 
 - Make sure you have the latest version of `R` and `RStudio`.
 
 - You may also need to install `Rtools`.
 
 - You can then run everything in Docker container `r emo::ji("love")`.
 
 - Kindly share your RMarkdown via our `Slack` channel.
 
 - There is also option to use `RStudio Cloud`.
 
 - Follow my instructions otherwise it will throw an `Error` `r emo::ji("ear")`.
 
 - Google is your best friend, the R community is huge.
 
 - read.csv, why not just import_csv?
 
 - You can get help by typing ? followed by the function name.

Those are typical statements that return potential `R` users back to regular spreadsheets. Let me tell you how.

A pro inExcl, SPSS, and other rlate GUI based applications are hugely discouraged by tese statements. I wish I could know the popuation of potential `R` users who drpped the package the first day because of one or more of the sentences listed above. They are jst so many out there.

# Conclusion

# References